Stack Safety as a Security Property

### 2020-09-10 rebuttal.txt

Reviewer C is particularly concerned with the way this work is
motivated. Our original goal in this work wasn't to formalize a stack safety
notion that is specific to micropolicies, but in hindsight we agree that the
result may appear to be tailored to that particular enforcement mechanism,
though we believe this is more a matter of presentation choices and
exposition-helping simplifications than a fundamental limitation. In
particular, we believe that the enforcement model can be used (with some
effort) to describe capability-based enforcement mechanisms, as we state in
Section 2.  However, given that this effort didn't make it into the final
product, we agree that the paper as it stands would be more accurately
described as an abstract property capturing micropolicy enforcement rather
than the all-encompassing stack safety notion we set out to state; we will
clarify this for a final version.

RELATED WORK

All reviewers also wanted additional discussion of related work.  We agree,
in particular, that there should be a clearer comparison to the two
Skorstengaard et al papers, using the five informal criteria proposed
there. We plan to include a discussion like the following:

(1) Intuitiveness:

The local state encapsulation (LSE) part of the
property we present aims to characterize stack safety in security
terms. For readers familiar with integrity / confidentiality /
noninterference, the eager version should be fairly intuitive. The
lazy/observable properties, though less intuitive, are more
interesting in that they precisely characterize behaviors that would
be considered violations to the more intuitive view of stack safety
but that can still be considered safe by an external observer. The
WBCF part simply formalizes standard behavior of stack-based control
flow.

@@

By contrast, Skorstengaard relies on different prior intuitions: for
readers familiar with the behavior of pure stacks (or rather the
built-in oLCM stack), their property is more intuitive. For readers
versed in security, we believe there is value in a different
perspective.

(2) Useful for reasoning:

In order to reason about actual programs we
would indeed need to incorporate a "Meaning of Memory Safety"-style
frame rule. Our goal with this paper was to distill the essence of
stack safety without adding the complex (but solved) overhead of
dealing with heap locations. But the properties (and the testing
framework behind it) were designed with [Azevedo et al] in mind.

BCP: I'm not sure this is hitting the right point.  Clearly, to reason about
programs with both stack and heap, we need something like that frame rule.
But the reviewer might wonder about how our property can be used for
_reasoning_ about programs with just a stack...
LEO: Isn't that the point of (4)? These criteria confuse me.

(3) reusable in compiler chains:

As reviewer C points out, this is not really applicable, since this is
a criterion tailored to what Skorstengaard is aiming to do. We might
consider what the equivalently tailored criterion would be for us --
usable in "dynamic enforcement environments" with potentially unsafe
commodity compilers.

(4) complete:

This criterion seems a bit circular. It asks for being
able to prove any property of a program that relies on stack safety
with a given characterization of stack safety - but we're in the
buisness of _defining_ stack safety in the first place. If the point
is that our definition should capture characteristics of established
informal notions of stack safety (subject to the limitations of the
language features our formalization supports - see 5), our properties
should apply to any such reasonable program.

(5) scalable:

Dynamic code would pose a significant challenge in this setup. In the
tag world, we could handle generated code by tagging the instructions
that generate it, which would correspond to a map that allows some
instructions to update the maps, including potentially itself.  On the
other hand, we described how we would handle coroutines, and threads
would be similar. Basically when we lose the monotonicity of contours
relative to stack depth, we will need to change the LSE property to
check integrity and confidentiality each time we cross between
security contexts - nested calls are not strictly more limited.

@@

We sketch how multiple threads/coroutines would work in the future
work section (l 1213-1219). In particular, we would need to further
distinguish stack locations as either "accessible" (current frame),
"belonging to the same call stack", or "belonging in another
stack". And then integrity would require that when a function changes
the locations in the "same" stack should be unchanged. Similarly for
cofnidentiality.

>  - In the future work section, the authors mentions several types of non-stack control flow that are not addressed by the current model, including tail calls. Other common non-stack control flow includes exceptions (such as c++ exceptions) and setjmp/longjmp. I understand that these non-stack control flow is more difficult to model, but for the exact reasons, how to formally characterize stack safety for these difficult cases becomes critical.

Tail calls were left out as it's only the characterization of the
return that poses a problem - once the point of context switch is
determined, the statement of stack safety remains largely the same.

BCP: Don't understand.  Are we saying tail calls are easy?  (Then why didn't
we just add them?)
LEO: It's much less clean in terms of the formalization and I thought
we had decided it wasn't worth the trouble - a sketch should be enough.

@@

> - The proposed notion of stack safety is too strong to be enforced by existing stack protection mechanisms.
>
>   [Roessler and DeHon 2018]'s "lazy tagging and clearing" is itself not stack-safe according to this paper.
>   To understand the mechanism, this paper additionally defines the "observable" versions of stack safety.
>   But then why you didn't use the observable version as the authoritative definition?

We propose two definitions of stack safety: one that is easier to understand
because it corresponds to a more naive view of what stack safety intuitively
means, and a slightly more complex and permissive one that (as Roessler and
Dehon showed) can be implemented more efficiently.  We believe both are of
interest.

> - This paper is lacking proper discussion on related work.
>
>    On the contrary to this paper's observation (L25), there're a few formalizations of stack safety (and rely/guarantee conditions for function invocation).
>       For example, see CompCert's assumption on function calls: https://github.com/AbsInt/CompCert/blob/94558ecb3e48261f12c644045d40c7d0784415e0/common/Events.v#L619

The CompCert specification cited here characterizes the assumptions
that the comiler correctness proof makes about the behavior of
external functions.  When taken together with other parts of the
CompCert spec that describe the block memory model and the treatment
of control stacks, this does imply some facts about the stack safety
conditions that CompCert assumes are provided by the external
environment. But it is certainly not intended as a general
characterization of stack safety, and it does not seem suitable as a
basis for checking validity of an enforcement mechanism.

@@

There is some relation.  E.g., the ec_readonly condition

  https://github.com/AbsInt/CompCert/blob/94558ecb3e48261f12c644045d40c7d0784415e0/common/Events.v#L651

looks related.  But CompCert's definition (a) doesn't protect the stack at
all from _reading_, and (b) isn't "nested" the way ours is.  This makes
sense, since C doesn't protect the stack!

Thanks for the pointer, we will make sure to include a discussion like this
in the revised version.

### 2020-09-10 rebuttal.txt

Thank you for the thoughtful comments.  We first discuss the most important
points raised, then, in an optional appendix, respond point-by-point to each
individual piece of reviewer feedback.

MOTIVATION

Reviewer C is particularly concerned with the way this work is
motivated. Our original goal in this work wasn't to formalize a stack safety
notion that is specific to micropolicies. In particular, we believe that the
enforcement model can be used (with some effort) to describe
capability-based enforcement mechanisms, as we state in Section 2.  In
retrospect we agree that our results may appear to be tailored to that
particular enforcement mechanism.

We believe this is more a matter of presentation choices and
exposition-helping simplifications than a fundamental limitation.  However,
given that a satisfying treatment of capability-based enforcement didn't
make it into the final product, we agree that the paper as it stands would
be more accurately described as an abstract property capturing micropolicy
enforcement rather than the all-encompassing stack safety notion we set out
to state; we will clarify this for a final version.

@@

By contrast, Skorstengaard relies on different prior intuitions: for
readers familiar with the behavior of pure stacks (or rather the
built-in oLCM stack), their property is more intuitive. For readers
versed in security, we believe there is value in a different
perspective.

(2) Usefulness for reasoning:

In order to reason about actual programs we
would indeed need to incorporate a "Meaning of Memory Safety"-style
frame rule. Our goal with this paper was to distill the essence of
stack safety without adding the complex (but solved) overhead of
dealing with heap locations. But the properties (and the testing
framework behind it) were designed with [Azevedo et al] in mind.

BCP: I'm not sure this is hitting the right point.  Clearly, to reason about
programs with both stack and heap, we need something like that frame rule.
But the reviewer might wonder about how our property can be used for
_reasoning_ about programs with just a stack...
LEO: Isn't that the point of (4)? These criteria confuse me.
BCP: Maybe 2 and 4 go together?  2 is about whether you can use it for
reasoning; 4 is about whether this reasoning is complete in the sense that
the proof principle is strong enough to prove safety of any safe program.

(3) Reusability in compiler chains:

@@

We sketch how multiple threads/coroutines would work in the future
work section (l 1213-1219). In particular, we would need to further
distinguish stack locations as either "accessible" (current frame),
"belonging to the same call stack", or "belonging in another
stack". And then integrity would require that when a function changes
the locations in the "same" stack should be unchanged. Similarly for
confidentiality.

>  - In the future work section, the authors mentions several types of non-stack control flow that are not addressed by the current model, including tail calls. Other common non-stack control flow includes exceptions (such as c++ exceptions) and setjmp/longjmp. I understand that these non-stack control flow is more difficult to model, but for the exact reasons, how to formally characterize stack safety for these difficult cases becomes critical.

We omitted tail calls as it's really only the characterization of the
return that poses a problem - once the point of context switch is
determined, the statement of stack safety remains largely the same.  We will
add a more detailed discussion.

### 2020-09-10 rebuttal.txt

RELATED WORK

All reviewers also wanted additional discussion of related work.  We agree,
in particular, that there should be a clearer comparison to the two
Skorstengaard et al papers, using the five informal criteria proposed
there. We plan to include a discussion like the following:

(1) Intuitiveness:

The local state encapsulation (LSE) part of the
property we present aims to characterize stack safety in security
terms. For readers familiar with integrity / confidentiality /
noninterference, the eager version should be fairly intuitive. The
lazy/observable properties, though less intuitive, are more
interesting in that they precisely characterize behaviors that would
be considered violations to the more intuitive view of stack safety
but that can still be considered safe by an external observer. The
well-bracketed control flow (WBCF) part simply formalizes standard
behavior of stack-based control flow.

By contrast, [Skorstengaard 2019b] relies on different prior intuitions: for
readers familiar with operational models of stacks (here the
built-in oLCM stack), their property is more intuitive. For readers
versed in security theory, we believe that making an explicit connection
with integrity and confidentiality gives useful insight.

@@

(2) Useful for reasoning:

In order to reason about actual programs we
would indeed need to incorporate a frame ruleMeaning of Memory Safety"-style
frame rule. Our goal with this paper was to distill the essence of
stack safety without adding the complex (but solved) overhead of
dealing with heap locations. But the properties (and the testing
framework behind it) were designed with [Azevedo et al 2018] in mind.

BCP: I'm not sure this is hitting the right point.  Clearly, to reason about
programs with both stack and heap, we need something like that frame rule.
But the reviewer might wonder about how our property can be used for
_reasoning_ about programs with just a stack...
LEO: Isn't that the point of (4)? These criteria confuse me.
APT: My take is that (2) is about what kind of programming logic
we can support, whereas (4) is about arguing that our definition
captures all the standard intuitions one might want to use in proofs.
I think the heap is a red herring here.

@@

As reviewer C points out, this is not really applicable, since this is
a criterion tailored to what Skorstengaard is aiming to do. We might
consider what the equivalently tailored criterion would be for us --
usable in "dynamic enforcement environments" with potentially unsafe
commodity compilers.

APT: I don't understand the last sentence.

(4) complete:

This criterion seems a bit circular. It asks for being
able to prove any property of a program that relies on stack safety
with a given characterization of stack safety - but we're in the
buisness of _defining_ stack safety in the first place. If the point
is that our definition should capture characteristics of established
informal notions of stack safety (subject to the limitations of the
language features our formalization supports - see 5), then we believe
it does.

### 2020-09-10 rebuttal.txt

All reviewers also wanted additional discussion of related work.  We agree,
in particular, that there should be a clearer comparison to the two
Skorstengaard et al papers, using the five informal criteria proposed
there. We plan to include a discussion like the following:

(1) Intuitiveness:

The local state encapsulation (LSE) part of the property we present aims to
characterize stack safety in security terms. For readers familiar with
integrity / confidentiality / noninterference, the eager version should be
fairly intuitive. The lazy/observable properties, though less intuitive, are
more interesting in that they precisely characterize behaviors that would be
considered violations to the more intuitive view of stack safety but that
can still be considered safe by an external observer. The WBCF part simply
formalizes standard behavior of stack-based control flow.

By contrast, [Skorstengaard 2019b] relies on different prior intuitions: for
readers familiar with operational models of stacks (here the
built-in oLCM stack), their property is more intuitive. For readers
versed in security theory, we believe that making an explicit connection
with integrity and confidentiality gives useful insight.

@@

(2) Usefulness for reasoning:

In order to reason about actual programs we
would indeed need to incorporate a frame ruleMeaning of Memory Safety"-style
frame rule. Our goal with this paper was to distill the essence of
stack safety without adding the complex (but solved) overhead of
dealing with heap locations. But the properties (and the testing
framework behind it) were designed with [Azevedo et al 2018] in mind.

BCP: I'm not sure this is hitting the right point.  Clearly, to reason about
programs with both stack and heap, we need something like that frame rule.
But the reviewer might wonder about how our property can be used for
_reasoning_ about programs with just a stack...
LEO: Isn't that the point of (4)? These criteria confuse me.
APT: My take is that (2) is about what kind of programming logic
we can support, whereas (4) is about arguing that our definition
captures all the standard intuitions one might want to use in proofs.
I think the heap is a red herring here.
BCP: Maybe 2 and 4 go together?  2 is about whether you can use it for
reasoning; 4 is about whether this reasoning is complete in the sense that
the proof principle is strong enough to prove safety of any safe program.

(3) reusable in compiler chains:

@@

As reviewer C points out, this is not really applicable, since this is
a criterion tailored to what Skorstengaard is aiming to do. We might
consider what the equivalently tailored criterion would be for us --
usable in "dynamic enforcement environments" with potentially unsafe
commodity compilers.

APT: I don't understand the last sentence.

(4) complete:

This criterion seems a bit circular. It asks for being
able to prove any property of a program that relies on stack safety
with a given characterization of stack safety - but we're in the
buisness of _defining_ stack safety in the first place. If the point
is that our definition should capture characteristics of established
informal notions of stack safety (subject to the limitations of the
language features our formalization supports - see 5), then we believe
it does.

(5) scalable:

### 2020-09-10 rebuttal.txt

We omitted tail calls as it's really only the characterization of the
return that poses a problem - once the point of context switch is
determined, the statement of stack safety remains largely the same.  We will
add a more detailed discussion.

>  [1] Xiaoyang Xu, Masoud Ghaffarinia, Wenhao Wang, Kevin W. Hamlen, and Zhiqiang Lin. 2019. CONFIRM: evaluating compatibility and relevance of control-flow integrity protections for modern software. In Proceedings of the 28th USENIX Conference on Security Symposium (SEC’19). USENIX Association, USA, 18051821.
>
> Comments for author
> -------------------
> Please see the weaknesses section.
>
>
>
> Review #27B
> ===========================================================================
>
> Overall merit
> -------------
> D. Strong Reject
>
> Reviewer expertise
> ------------------
> Y. Knowledgeable
>
> Paper summary
> -------------
> This paper:
> - Defines stack safety as confidentiality, integrity, and well-bracketedness.
> - Evaluates existing stack protection mechanisms w.r.t. the defined notion of stack safety.
> - Proposes other protection mechanisms.
>
> Strengths
> ---------
> - This paper is clearly defining a notion of stack safety.
>
> Weaknesses
> ----------
> - The proposed notion of stack safety is too strong to be used for real-world programs.
> - The proposed notion of stack safety is too strong to be enforced by existing stack protection mechanisms.
> - This paper is lacking proper discussion on related work.
>
> Comments for author
> -------------------
> This paper is not clearly motivated, and as a result, has the following problems:
>
> - The proposed notion of stack safety is too strong to be used for real-world programs.
>
>   As discussed in Section 9, stack-derived pointers are not supported (L1199), but they are widely used in real-world programs.
>   Furthermore, without stack-derived pointers, stack safety is more-or-less obvious to define.

Stack-derived pointers are not supported yet, but based on the sketch in future work (L1199+)
we feel it is relatively straightforward combination of known techniques (on top of the
definition of the properties we introduced).

APT: Does Sk2019b support stack-derived pointers? I don't think so, although I'm not certain.
LEO: This reviewer doesn't complain about Sk2019b - maybe not make reviewer C look at this even more closely by invoking that?

@@

>   - dynamic code generation (seems problematic for the function map, call map and return map)
>   - dynamic linking (seems problematic for the function map, call map and return map)
>   - self-editing code (seems problematic for call map and return map)

These three extensions would indeed be challenging. We could
potentially handle generated code by using special contours for the
instructions that generate it, which would correspond to a map that
allows some instructions to update the maps, including potentially the
map itself.

BCP: I don't actually believe the second sentence.

>   - tail calls (seems potentially okay, but I'd like to be sure)
>   - exceptions and stack unwinding

We believe so. The (minor) problem with tail calls is characterizing
the return - once the point of context switch is determined, the
statement of stack safety remains largely the same. Notably a tail
call's return point is shared with its caller, so if the
(non-tail-call) caller obeys Return Integrity, the expected control
flow of the tail call is already captured. Exceptions would be
slightly trickier, but could potentially be handled by multiple
allowable return points (e.g. one for the call and one for the
exception handler).

### 2020-09-10 rebuttal.txt

BCP (OLD): Maybe 2 and 4 go together?  2 is about whether you can use it for
reasoning; 4 is about whether this reasoning is complete in the sense that
the proof principle is strong enough to prove safety of any safe program.

(3) reusable in compiler chains:

As reviewer C points out, this is not really applicable, since this is
a criterion tailored to what Skorstengaard is aiming to do. We might
consider what the equivalently tailored criterion would be for us --
usable in "dynamic enforcement environments" with potentially unsafe
commodity compilers.

SNA: trying to phrase this better.
A more general version of this criterion might be, "Is the model suitable
for a practical application in the engineering of secure systems?"
In our case, such an application would be use in "dynamic enforcement
environments" with code generated by non-secure compilation, ideally
with commodity compilers.

@@

(4) complete:

This criterion seems a bit circular. It asks for being
able to prove any property of a program that relies on stack safety
with a given characterization of stack safety - but we're in the
buisness of _defining_ stack safety in the first place. If the point
is that our definition should capture characteristics of established
informal notions of stack safety (subject to the limitations of the
language features our formalization supports - see 5), then we believe
it does.

(5) scalable:

Dynamic code would pose a significant challenge in this setup. In the
tag world, we could handle generated code by tagging the instructions
that generate it, which would correspond to a map that allows some
instructions to update the maps, including potentially itself.

SNA: how about...

Dynamic code would pose a significant challenge in this setting.
Our various maps would need to be made dynamic, which would require
either very restricted code modification or very complex machinery.
It would also raise questions about how to handle all of our trace
properties when (for instance) a return map might change mid-call.
Substantial rethinking of both the machinery and the property statements
themselves make this an unlikely feature to add.

On the other hand, we described how we would handle coroutines, and threads
would be similar. Basically when we lose the monotonicity of contours
relative to stack depth, we will need to change the LSE property to
check integrity and confidentiality each time we cross between
security contexts - nested calls are not strictly more limited than
their callers.

Loss of monotonicity, and the attendant changes in the LSE property,
are a consistent theme among potential expansions to the model.
Stack-derived pointers, as described in Section 9, are a natural
extension of the model that will give up monotonicity.

### 2020-09-10 rebuttal.txt

Thank you for the thoughtful comments.  We first discuss the most important
points raised, then, in an optional appendix, respond point-by-point to each
individual piece of reviewer feedback.

MOTIVATION

Reviewer C is particularly concerned with the way this work is
motivated. Our original goal in this work was to formalize a stack
safety notion that applies to many enforcement mechanisms, not just to
micropolicies.  In particular, we believe that the enforcement model
can be used (with some effort) to describe capability-based
enforcement mechanisms, as we state in Section 2.  But in retrospect
we agree that our results may appear to be tailored to micropolicies.

We believe this is more a matter of presentation choices and
simplifications intended to help exposition than a fundamental limitation.  However,
given that a satisfying treatment of capability-based enforcement didn't
make it into the final product, we agree that the paper as it stands would
be more accurately described as an abstract property capturing micropolicy
enforcement rather than the all-encompassing stack safety notion we set out
to state; we will clarify this for a final version.

APT: Not to beat a dead horse, but this seems to completely throw away
our claim that security theory ideas are useful for characterizing
stack safety.  Could we incorporate that point somewhere in the above?

@@

RELATED WORK

All reviewers also wanted additional discussion of related work.  We agree,
in particular, that there should be a clearer comparison to the two
Skorstengaard et al papers, using the five informal criteria proposed
there. We plan to include a discussion like the following:

(1) Intuitiveness:

The local state encapsulation (LSE) part of the property we present
aims to characterize stack safety in security terms. For readers
familiar with integrity / confidentiality / noninterference, the eager
version should be fairly intuitive. The lazy/observable properties,
though less intuitive, are more interesting in that they precisely
characterize behaviors that would be considered violations to the more
intuitive view of stack safety but that can still be considered safe
by an external observer. The well-bracketec control flow (WBCF) part
simply formalizes standard behavior of stack-based control flow.

@@

By contrast, [Skorstengaard 2019b] relies on different prior intuitions: for
readers familiar with operational models of stacks (here the
built-in oLCM stack), their property is more intuitive. For readers
versed in security theory, we believe that making an explicit connection
with integrity and confidentiality gives useful insight.

(2) Usefulness for reasoning:

In order to reason about actual programs we
would indeed need to incorporate a "Meaning of Memory Safety"-style
frame rule. Our goal with this paper was to distill the essence of
stack safety without adding the complex (but solved) overhead of
dealing with heap locations. But the properties (and the testing
framework behind it) were designed with [Azevedo et al 2018] in mind.

BCP: I'm not sure this is hitting the right point.  Clearly, to reason about
programs with both stack and heap, we need something like that frame rule.
But the reviewer might wonder about how our property can be used for
_reasoning_ about programs with just a stack...
LEO: Isn't that the point of (4)? These criteria confuse me.
APT: My take is that (2) is about what kind of programming logic
we can support, whereas (4) is about arguing that our definition
captures all the standard intuitions one might want to use in proofs.
I think the heap is a red herring here.
BCP: Agree

BCP (OLD): Maybe 2 and 4 go together?  2 is about whether you can use it for
reasoning; 4 is about whether this reasoning is complete in the sense that
the proof principle is strong enough to prove safety of any safe program.

@@

(3) reusable in compiler chains:

As reviewer C points out, this is not really applicable, since this is
a criterion tailored to what Skorstengaard et al. are aiming to do. We might
consider what the equivalently tailored criterion would be for us --
usable in "dynamic enforcement environments" with potentially unsafe
commodity compilers.

### 2020-09-10 rebuttal.txt

The local state encapsulation (LSE) part of the property we present
aims to characterize stack safety in security terms. For readers
familiar with integrity / confidentiality / noninterference, the eager
version should be fairly intuitive. The lazy/observable properties,
though less intuitive, are more interesting in that they precisely
characterize behaviors that would be considered violations to the more
intuitive view of stack safety but that can still be considered safe
by an external observer. The well-bracketec control flow (WBCF) part
simply formalizes standard behavior of stack-based control flow.

By contrast, [Skorstengaard 2019b] relies on different prior intuitions: for
readers familiar with operational models of stacks (here the
built-in oLCM stack), their property is more intuitive. For readers
versed in security theory, we believe that making an explicit connection
with integrity and confidentiality gives useful insight.

(2) Usefulness for reasoning:

In order to reason about actual programs we
would indeed need to incorporate a "Meaning of Memory Safety"-style
frame rule. Our goal with this paper was to distill the essence of
stack safety without adding the complex (but solved) overhead of
dealing with heap locations. But the properties (and the testing
framework behind it) were designed with [Azevedo et al 2018] in mind.

### 2020-09-10 rebuttal.txt

This criterion seems a bit circular. It asks for being
able to prove any property of a program that relies on stack safety
with a given characterization of stack safety - but we're in the
buisness of _defining_ stack safety in the first place. If the point
is that our definition should capture characteristics of established
informal notions of stack safety (subject to the limitations of the
language features our formalization supports - see 5), then we believe
it does.

(5) scalable:

Dynamic code would pose a significant challenge in this setting.
Our various maps would need to be made dynamic, which would require
either very restricted code modification or very complex machinery.
It would also raise questions about how to handle all of our trace
properties when (for instance) a return map might change mid-call.
Substantial rethinking of both the machinery and the property statements
themselves make this an unlikely feature to add.

On the other hand, we described how we would handle coroutines, and threads
would be similar. Basically when we lose the monotonicity of contours
relative to stack depth, we will need to change the LSE property to
check integrity and confidentiality each time we cross between
security contexts - nested calls are no longer strictly more limited than
their callers.

### 2020-09-10 rebuttal.txt

RELATED WORK

All reviewers also wanted additional discussion of related work.  We agree,
in particular, that there should be a clearer comparison to the two
Skorstengaard et al papers, using the five informal criteria proposed
there. We plan to include a discussion like the following:

(1) Intuitiveness:

The local state encapsulation (LSE) part of the property we present aims to
characterize stack safety in security terms. For readers familiar with
integrity / confidentiality / noninterference, the eager version should be
fairly intuitive. The lazy/observable properties, though less intuitive, are
more interesting in that they precisely characterize behaviors that would be
considered violations to the more intuitive view of stack safety but that
can still be considered safe by an external observer. The WBCF part simply
formalizes standard behavior of stack-based control flow.

@@

By contrast, [Skorstengaard 2019b] relies on different prior intuitions: for
readers familiar with operational models of stacks (here the
built-in oLCM stack), their property is more intuitive. For readers
versed in security theory, we believe that making an explicit connection
with integrity and confidentiality gives useful insight.

(2) Usefulness for reasoning:

In order to reason about actual programs we
would indeed need to incorporate a frame ruleMeaning of Memory Safety"-style
frame rule. Our goal with this paper was to distill the essence of
stack safety without adding the complex (but solved) overhead of
dealing with heap locations. But the properties (and the testing
framework behind it) were designed with [Azevedo et al 2018] in mind.

@@

BCP: I'm not sure this is hitting the right point.  Clearly, to reason about
programs with both stack and heap, we need something like that frame rule.
But the reviewer might wonder about how our property can be used for
_reasoning_ about programs with just a stack...
LEO: Isn't that the point of (4)? These criteria confuse me.
APT: My take is that (2) is about what kind of programming logic
we can support, whereas (4) is about arguing that our definition
captures all the standard intuitions one might want to use in proofs.
I think the heap is a red herring here.
BCP: Agree

BCP (OLD): Maybe 2 and 4 go together?  2 is about whether you can use it for
reasoning; 4 is about whether this reasoning is complete in the sense that
the proof principle is strong enough to prove safety of any safe program.

(3) reusable in compiler chains:

As reviewer C points out, this is not really applicable, since this is
a criterion tailored to what Skorstengaard is aiming to do. We might
consider what the equivalently tailored criterion would be for us --
usable in "dynamic enforcement environments" with potentially unsafe
commodity compilers.

@@

We believe this extension is possible.

The call map serves two purposes: identifying call points and allowing for
an easy calculation of the stack pointer at the time of the call. We could
keep the call map essentially as a set and use a frame pointer (or a similar
abstraction) for the latter functionality.  Keeping the number of arguments
in the map is certainly convenient, but not necessary.

>   - dynamic code generation (seems problematic for the function map, call map and return map)
>   - dynamic linking (seems problematic for the function map, call map and return map)
>   - self-editing code (seems problematic for call map and return map)

As discussed in the toplevel summary, for criterion (5), these three
extensions would indeed be challenging.

### 2020-09-10 rebuttal.txt

By contrast, [Skorstengaard 2019b] relies on different prior intuitions: for
readers familiar with operational models of stacks (here the
built-in oLCM stack), their property is more intuitive. For readers
versed in security theory, we believe that making an explicit connection
with integrity and confidentiality gives useful insight.

(2) Usefulness for reasoning:

In order to reason about actual programs we
would indeed need to incorporate a "Meaning of Memory Safety"-style
frame rule. Our goal with this paper was to distill the essence of
stack safety without adding the complex (but solved) overhead of
dealing with heap locations. But the properties (and the testing
framework behind it) were designed with [Azevedo et al 2018] in mind.

APT: Leo asks: "what kind of logic do we want to claim to support?"
I dunno, a Hoare logic with some simple procedure rule?
Integrity says that local variables do not change over calls,
which basically says that procedure calls are a no-op (except
for the return value).  Confidentiality says that lemmas proved about
procedure return values can be applied at call sites.

### 2020-09-10 rebuttal.txt

The local state encapsulation (LSE) part of the property we present aims to
characterize stack safety in security terms. For readers familiar with
integrity / confidentiality / noninterference, the eager version should be
fairly intuitive. The lazy/observable properties, though less intuitive, are
more interesting in that they precisely characterize behaviors that would be
considered violations to the more intuitive view of stack safety but that
can still be considered safe by an external observer. The WBCF part simply
formalizes standard behavior of stack-based control flow.

By contrast, [Skorstengaard 2019b] relies on different prior intuitions: for
readers familiar with operational models of stacks (here the
built-in oLCM stack), their property is more intuitive. For readers
versed in security theory, we believe that making an explicit connection
with integrity and confidentiality gives useful insight.

(2) Usefulness for reasoning:

Local state encapsulation enables reasoning about the behavior of a function
in a vacuum, without needing to account for either its caller's state or
for changes to its state during its callees. Without confidentiality,
proving a property of a function requires a quantification over all possible
configurations of memory. With confidentiality, only all possible configurations
of the stack frame itself need be considered.

As for integrity, our threat model permits a callee to execute arbitrary code,
severely limiting our ability to reason about the behavior of its caller after
return. But we can now prove properties of the caller by quantifying only over
configurations of registers and memory above the stack. In security terms, we
make no guarantees about the callee's behavior, but we can guarantee that it
communicates with the caller only through the approved interface.

Meanwhile, WBCF enables reasoning about the whole structure of the program
in terms of predictable control flows between its components.

SNA: I feel like it would be good to be less informal and put this in programming
     logic terms, but I'm not familiar enough with the language. Also we didn't
     formalize a programming logic, so I'm not sure how much we can say formally.

------- old -------

@@

(4) complete:

This criterion seems a bit circular. It asks for being
able to prove any property of a program that relies on stack safety
with a given characterization of stack safety - but we're in the
buisness of _defining_ stack safety in the first place. If the point
is that our definition should capture characteristics of established
informal notions of stack safety (subject to the limitations of the
language features our formalization supports - see 5), then we believe
it does.

(5) scalable:

Dynamic code would pose a significant challenge in this setup. In the
tag world, we could handle generated code by tagging the instructions
that generate it, which would correspond to a map that allows some
instructions to update the maps, including potentially itself.

SNA: how about...

@@

> * What exactly is the benefit of your approach to defining stack safety w.r.t. the approach of Skorstengaard 2019b?
>   Do you think it can be applied to more or less languages?
>   Do you think it is better suited or less well suited for reasoning about programs which depend on stack safety?
>   Do you think it is etc.

See the full comparison in terms of the criteria in the summary.

> * Do you think you could show safety of a specific example program that depends on stack safety (like the awkward example) and if so, how would such a proof work?

LEO: This is the (4) criterion I guess again. I'm not sure exactly what this means.
APT: I agree with SNA that this is the (2) criterion. Maybe we could doctor up the example program to
include some external call to an adversary and sketch how it we would use it to prove
that it still prints 0, 60 (or whatever).

BCP: I think this is a more focused question: Suppose you had a program that
you believed was correct according to this criterion and you wanted to prove
that it was.  How would the proof look?

@@

We believe this extension is possible.

The call map serves two purposes: identifying call points and allowing for
an easy calculation of the stack pointer at the time of the call. We could
keep the call map essentially as a set and use a frame pointer (or a similar
abstraction) for the latter functionality.  Keeping the number of arguments
in the map is certainly convenient, but not necessary.

>   - dynamic code generation (seems problematic for the function map, call map and return map)
>   - dynamic linking (seems problematic for the function map, call map and return map)
>   - self-editing code (seems problematic for call map and return map)

These three extensions would indeed be challenging. Our static maps would need
to be replaced with more dynamic machinery, likely becoming either very complex
or much more concrete about what constitutes a call, return, etc.

### 2020-09-10 rebuttal.txt

In order to reason about actual programs we
would indeed need to incorporate a "Meaning of Memory Safety"-style
frame rule. Our goal with this paper was to distill the essence of
stack safety without adding the complex (but solved) overhead of
dealing with heap locations. But the properties (and the testing
framework behind it) were designed with [Azevedo et al 2018] in mind.

APT: Leo asks: "what kind of logic do we want to claim to support?"
I dunno, a Hoare logic with some simple procedure rule?
Integrity says that local variables do not change over calls,
which basically says that procedure calls are a no-op (except
for the return value).  Confidentiality says that lemmas proved about
procedure return values can be applied at call sites.

BCP: I'm not sure this is hitting the right point.  Clearly, to reason about
programs with both stack and heap, we need something like that frame rule.
But the reviewer might wonder about how our property can be used for
_reasoning_ about programs with just a stack...
LEO: Isn't that the point of (4)? These criteria confuse me.
APT: My take is that (2) is about what kind of programming logic
we can support, whereas (4) is about arguing that our definition
captures all the standard intuitions one might want to use in proofs.
I think the heap is a red herring here.
BCP: Agree

BCP: I think we should rewrite the point to simply speculate that something
analogous to the frame rule from the "meaning of memory safety" paper could
be developed here for the stack.

### 2020-09-10 rebuttal.txt

The local state encapsulation (LSE) part of the property we present
aims to characterize stack safety in security terms. For readers
familiar with integrity / confidentiality / noninterference, the eager
version should be fairly intuitive. The lazy/observable properties,
though less intuitive, are more interesting in that they precisely
characterize behaviors that would be considered violations to the more
intuitive view of stack safety but that can still be considered safe
by an external observer. The well-bracketec control flow (WBCF) part
simply formalizes standard behavior of stack-based control flow.

By contrast, [Skorstengaard 2019b] relies on different prior intuitions: for
readers familiar with operational models of stacks (here the
built-in oLCM stack), their property is more intuitive. For readers
versed in security theory, we believe that making an explicit connection
with integrity and confidentiality gives useful insight.

(2) Usefulness for reasoning:

Local state encapsulation enables reasoning about the behavior of a
function in a vacuum, without needing to account for either its
caller's state or for changes to its state during its callees. When
proving a property of a function, confidentiality allows us to only
reason about configurations of the stack frame itself (instead of all
possible _memory_ configurations).  As for integrity, our threat model
permits a callee to execute arbitrary code, severely limiting our
ability to reason about the behavior of its caller after return. But
we can now prove properties of the caller by quantifying only over
configurations of registers and memory above the stack.

In security terms, we make no guarantees about the callee's behavior,
but we can guarantee that it communicates with the caller only through
the approved interface.  In terms of a logic, integrity and
confidentiality would allow a procedure rule that states that local
variables do not change over calls, (which basically says that
procedure calls are a no-op except for the return value) and that
lemmas proved about procedure return values can be applied at call
sites.

### 2020-09-10 rebuttal.txt

Thank you for the thoughtful comments.  We first discuss the most important
points raised, then, in an optional appendix, respond point-by-point to each
individual piece of reviewer feedback.

MOTIVATION

Reviewer C is particularly concerned with the way this work is
motivated. Our original goal in this work was to formalize a stack
safety notion that applies to many enforcement mechanisms, not just to
micropolicies.  In particular, we believe that the enforcement model
can be used (with some effort) to describe capability-based
enforcement mechanisms, as we state in Section 2.  But in retrospect
we agree that our results may appear to be tailored to micropolicies.

We believe this is more a matter of presentation choices and
simplifications intended to help exposition than a fundamental
limitation.  However, given that a satisfying treatment of
capability-based enforcement didn't make it into the final product, we
agree that the paper as it stands would be more accurately described
as an abstract property capturing micropolicy enforcement rather than
the all-encompassing stack safety notion we set out to state; we will
clarify this for a final version. We still maintain that security
theory ideas are are useful and interesting for characterizing stack
safety, but we will restrict our claims to the micropolicy setting.
